### 2014-03-05 src/paper.Rnw

@@

<<results='asis'>>=
o <- subset(stats.df, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(stats.df, kind == 'randoop')
r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
@

>>>>

\subsection{Probes}
% half_per_line half_per_method :  + halfrand-project
%   For each (line|method|class), get the number of mutants produced. Then sample exactly half the mutants produced per unit

@@

<<results='asis'>>=
o <- subset(stats.df, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(stats.df, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
@
